\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{cmap} % Search in PDF
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry} % Простой способ задавать поля
    		\geometry{top=20mm}
    		\geometry{bottom=20mm}
    		\geometry{left=25mm}
    		\geometry{right=25mm}
\usepackage{url,multicol}
% \setlength{\columnsep}{0.6cm}
%------------------

\begin{document}
	
\title{My Heart Christ's Home}
\author{Robert Boyd Munger}
\date{1951}
\maketitle

\begin{abstract}
    Robert Boyd Munger (1911-2001) has served numerous pastorates and as a~professor of Evangelism and Church Strategy at Fuller Theological Seminary.
\end{abstract}

    \begin{quote}
    “Robert Boyd Munger was a~Presbyterian minister who wrote this timeless work in 1951. It was a~vividly compelling then, and I~have found no other essay on the ABC's of the Christian life, other than Scripture itself, so impacting as Munger's wonderful work still today.” 
    (Quote from a~Christian leader)
    \end{quote}

\vspace{1cm}


\begin{multicols}{2}

In Paul's epistle to the Ephesians, we find these words: 

\begin{quote}
"That (God) would grant you, according to the riches of 
his glory, to be strengthened with might by his Spirit in 
the inner man; That Christ may dwell in your hearts by 
faith" (Ephesians 3:16).
\end{quote}

Or, as another has translated, 

\begin{quote}
"That Christ may settle down and be at home in your 
hearts by faith." 
\end{quote}

Without question one of the most remarkable Christian doctrines is that Jesus Christ Himself through the presence of the Holy Spirit will actually enter a~heart, settle down and be at home there. Christ will make the 
human heart His abode. 

Our Lord said to His disciples, "If a~man love me, he will keep my words: and my Father will love him, and we will come unto him, and make our abode with him"~(John 14:23). It was difficult for them to understand what He was saying. How was it possible for Him to make his abode with them in this sense? 

It is interesting that our Lord used the same word here that He gave them in the first of the fourteenth chapter of John: "I~go to prepare a~place for you .. that where I~am, ye may be also." Our Lord was promising his disciples that, just as He was going to heaven to prepare a~place for them and would welcome them one day, now it would be possible for them to prepare a~place for Him in their hearts and He would come and make His abode with them. 

They could not understand this. How could it be? 

Then came Pentecost. The Spirit of the living Christ was given to the church and they understood. God did not dwell in Herod's temple in Jerusalem! God did not dwell in a~temple made with hands; but now, through the miracle of the outpoured Spirit, God would dwell in human hearts. The body of the believer would be the temple of the living God and the human heart would be the home of Jesus Christ. It is difficult for me to think of a~higher privilege than to make Christ a~home in my heart, to welcome, to serve, to please, to fellowship with him there. 

One evening I~invited Jesus Christ into my heart. What an entrance He made! It was not a~spectacular, emotional thing, but very real. It was at the very center of my life. He came into the darkness of my heart and turned on the light. He built a~fire in the cold hearth and banished the chill. He started music where there had been stillness, and He filled the emptiness with His own loving, wonderful fellowship. I~have never regretted opening the door to Christ and I~never will~--- not into eternity! 

This, of course, is the first step in making the heart Christ's home. He has said, "Behold I~stand at the door and knock: if any man hear my voice and open the door, I~will come in to him, and will sup with him, and he with me."~(Revelation 3:20). If you are interested in making your life an abode of 
the living God, let me encourage you to invite Christ into your heart and He will surely come. 

After Christ entered my heart and in the joy of this new relationship I~said to Him, "Lord, I~want this heart of mine to be Yours. I~want to have You settle down here and be perfectly at home. Everything I~have belongs to You. Let me show You around and introduce you to the various features of the home that you may be more comfortable and that we may have fuller fellowship 
together." 

He was very glad to come, of course, and happier still to be given a~place in the heart.
\end{multicols}

\begin{multicols}{2}
    [
\section*{The Library}
    ]

The first room was the study~---the library. Let us call it the study of the mind. Now in my home this room of the mind is a~very small room with very thick walls. But it is an important room. In a~sense, it is the control room of the house. He entered with me and looked around at the books in the bookcase, the magazines upon the table, the pictures on the walls. As I~followed His gaze I~became uncomfortable. Strangely enough, I~had not felt badly about this before, but now that He was there looking at these things I~was embarrassed. There were some books were there that His eyes were too pure to behold. There was a~lot of trash and literature on the table that a~Christian had no business reading, and as for the pictures on the walls~---the imaginations and thoughts of the mind~--- these were shameful. 

I~turned to Him and said, "Master, I~know that this room needs a~radical alteration. Will You help me make it what it ought to be?~---to bring every thought into captivity to you?" 

"Surely!" He said. "Gladly will I~help you. First of all, take all the things that you are reading and looking at which are not helpful, pure, good and true, and throw them out! Now put on the empty shelves the books of the Bible. Till the library with Scriptures and meditate on then day and night. 

As for the pictures on the walls, you will have difficulty controlling these images, but here is an aid" He gave me a~full-size portrait of Himself. "Hang this centrally," He said, "on the wall of the mind." 

I~did, and I~have discovered through the years that when my thoughts are centered upon Christ Himself, His purity and power cause impure thoughts to back away. So He has helped me to bring my thoughts into captivity. 

May I~suggest to you if you have difficulty with this little room of the mind, that you bring Christ in there. Pack it full with the Word of God, meditate upon it and keep before it the immediate presence of the Lord Jesus. 
\end{multicols}

\begin{multicols}{2}
    [
\section*{The Dining Room}
    ]

From the study we went into the dining room, the room of appetites and desires. Now this was a~very large room. I~spent a~good deal of time in the dining room and much effort in satisfying my wants. 

I~said to Him, "This is a~favorite room. I~am quite sure You will be pleased with what we serve." 

He seated Himself at the table with me and asked, "What is on the menu for dinner?" 

"Well," I~said, "my favorite dishes: money, academic degrees and stocks, with newspaper articles of fame and fortune as side dishes." These were the things I~liked~---worldly fare. I~suppose there was nothing radically wrong in any particular item, but it was not the food that should satisfy the life of a~real Christian. When the food was placed before Him, He said nothing about it. However, I~observed that He did not eat it, and I~said to Him, somewhat disturbed, "Master, don't You care for this food? What is the trouble?" 

He answered, "I~have meat to eat that you do not know of. My meat is to do the will of Him that sent Me." He looked at me again and said, "If you want food that really satisfies you, seek the will of the Father, not your own pleasures, not your own desires, and not your own satisfaction. Seek to please Me and that food will satisfy you." And there at the table He gave me a~taste of doing God's will. What a~flavor! There is no food like it in all the world. It alone satisfies. Everything else is dissatisfying in the end. 

Now if Christ is in your heart, and I~trust He is, what kind of food are you serving Him and what kind of food are you eating yourself? Are you living for the lust of the flesh and the pride of life~--- selfishly? Or are you choosing God's will for your meat and drink? 
\end{multicols}


\begin{multicols}{2}
    [
\section*{The Living Room}
    ]
We walked next into the living room. This room was rather intimate and comfortable. I~liked it. It had a~fireplace, overstuffed chairs, a~sofa, and a~quiet atmosphere. 

He also seemed pleased with it. He said, "This is indeed a~delightful room. Let us come here often. 

It is secluded and quiet, and we can fellowship together." 

Well, naturally as a~young Christian I~was thrilled. I~couldn't think of anything I~would rather do than have a~few minutes with Christ in intimate companionship. 

He promised, "I~will be here early every morning. Meet me here, and we will start the day together." 

So morning after morning, I~would come downstairs to the living room and He would take a~book of the Bible from the bookcase. He would open it and then we would read together. He would tell me of its riches and unfold to me its truths. He would make my heart warm as He revealed His love and His grace He had toward me. These were wonderful hours together. In fact, we called the living room the "withdrawing room." It was a~period when we had our quiet time together. 

But, little by little, under the pressure of many responsibilities, this time began to be shortened. 

Why, I'm don't know, but I~thought I~was just too busy to spend time with Christ. This was not intentional, you understand; it just happened that way. Finally, not only was the time shortened, but I~began to miss a~day now and then. It was examination time at the university. Then it was some other urgent emergency. I~would miss it two days in a~row and often more. 


I~remember one morning when I~was in a~hurry, rushing downstairs, eager to be on my way. 

As I~passed the living room, the door was open. Looking in, I~saw a~fire in the fireplace and Jesus was sitting there. Suddenly in dismay I~thought to myself, "He was my guest. I~invited Him into my heart! He has come as Lord of my home. And yet here I~am neglecting Him." 

I~turned and went in. With downcast glance, I~said, "Blessed Master, forgive me. Have You been here all these mornings?" 

"Yes," He said, "I~told you I~would be here every morning to meet with you." Then I~was even more ashamed. He had been faithful in spite of my faithfulness. I~asked His forgiveness and He readily forgave me as He does when we are truly repentant. 

"The trouble with you is this: you have been thinking of the quiet time, of the Bible study and prayer time, as a~factor in your own spiritual progress, but you have forgotten that this hour means something to me also. Remember, I~love you. I~have redeemed you at great cost. I~value your fellowship. Now," He said, "do not neglect this hour if only for my sake. Whatever else may be your desire, remember I~want your fellowship!" 

You know, the truth that Christ desires my companionship, that He loves me, wants me to be with Him, wants to be with me and waits for me, has done more to transform my quiet time with God than any other single fact. Don't let Christ wait alone in the living room of your heart, but every day find some time when, with your Bible and in prayer, you may be together with Him. 
\end{multicols}

\begin{multicols}{2}
    [
\section*{The Workroom}
    ]
Before long, He asked, "Do you have a~workroom in your home?" Down in the basement of the home of my heart I~had a~workbench and some equipment, but I~was not doing much with it. Once in a~while I~would play around with a~few little gadgets, but I~wasn't producing anything substantial or worthwhile. 

I~led Him down there. 

He looked over the workbench and what little talents and skills I~had. He said, "This is quite well furnished. What are you producing with your life for the Kingdom of God?" He looked at one or two little toys that I~had thrown together on the bench and held one up to me. "Are these little toys 
all that you are doing for others in your Christian life?" 

"Well," I~said, "Lord, that is the best I~can do. I~know it isn't much, and I~really want to do more, but after all, I~have no skill or strength to do more." 

"Would you like to do better?" He asked. 

"Certainly," I~replied. 

"All right. Let me have your hands. Now relax in me and let my Spirit work through you. I~know that you are unskilled, clumsy and awkward, but the Holy Spirit is the Master-Worker, and if He controls your hands and your heart, He will work through you." And so, stepping around behind me and putting His great, strong hands over mine, controlling the tools with His skilled fingers He began to work through me. 

There's much more that I~must still learn and I~am very far from satisfied with the product that is being turned out, but I~do know that whatever has been produced for God has been through His strong hand and through the power of His Spirit in me. 

Do not become discouraged because you cannot do much for God. Your ability is not the fundamental condition. It is He who is controlling your fingers and upon whom you are relying. Give your talents and gifts to God and He will do things with them that will surprise you.. 
\end{multicols}


\begin{multicols}{2}
    [
\section*{The Rec Room}
    ]
I~remember the time He asked me about the playroom. I~was hoping He would not ask about that. There were certain associations and friendships, activities and amusements that I~wanted to keep for myself. I~did not think Christ would enjoy them or approve of them, so I~evaded the question. 

But there came an evening when I~was on my way out with some of my friends, and as I~was about to cross the threshold, He stopped me with a~glance and asked, "Are you going out?" 

I~replied, "Yes." 

"Good," He said, "I~would like to go with you." 

"Oh," I~answered rather awkwardly. "I~don't think, Lord Jesus, that You would really want to go with us. Let's go out tomorrow night. Tomorrow night we will go to prayer meeting, but tonight I~have another appointment." 

He said. "That's alright. Only I~thought that when I~came into your home, we were going to do everything together, to be close companions. I~just want you to know that I~am willing to go with you." 

"Well," I~said, "we will go someplace together tomorrow night." 

That evening I~spent some miserable hours. I~felt wretched. What kind of a~friend was I~to Jesus when I~was deliberately leaving Him out of my associations, doing things and going places that I~knew very well He would not enjoy? When I~returned that evening, there was a~light in His room, 
and I~went up to talk it over with Him. I~said, "Lord, I~have learned my lesson. I~can't have a~good time without You. From now on we will do everything together." 

Then we went down into the playroom of the house and He transformed it. He brought into life real joy, real happiness, real satisfaction, new friends, new excitement, new joys. Laughter and music have been ringing through the house ever since. 
\end{multicols}


\begin{multicols}{2}
    [
\section*{The Hall Closet}
    ]
There is just one more matter that I~might share with you. One day I~found Him waiting for me at the door. An arresting look was in His eye. As I~entered, He said to me, "There is a~peculiar odor in the house. There is something dead around here. It's upstairs. I~think it is in the hall closet." As soon as He said this, I~knew what He was talking about. Yes, there was a~small closet up there on the landing, just a~few feet square, and in that closet, behind lock and key, I~had one or two little personal things that I~did not want anyone to know about and certainly I~did not want Christ to see them. I~knew they were dead and rotting things left over from the old life. And yet I~loved them, and I~wanted them so for myself that I~was afraid to admit they were there. 

Reluctantly, I~went up with Him, and as we mounted the stairs the odor became stronger and stronger. He pointed at the door. "It's in there! Some dead thing!" 

I~was angry. That's the only way I~can put it. I~had given Him access to the library, the dining room, the living room, the workroom, the playroom, and now He was asking me about a~little two-by-four closet. I~said to myself, "This is too much. I~am not going to give Him the key." 

"Well," He said, reading my thoughts, "if you think I'm going to stay up here on the second floor with this odor, you are mistaken. I~will take my bed out on the back porch. I'm certainly not going to put up with that." Then I~saw Him start down the stairs. 

When you have come to know and love Christ, the worst thing that can happen is to sense His fellowship retreating from you. I~had to surrender. "I'll give You the key," I~said sadly, "but You'll have to open the closet and clean it out. I~haven't the strength to do it." 

"I~know," He said. "I~know you haven't. Just give me the key. Just authorize me to take care of that closet and I~will." So with trembling fingers I~passed the key to Him. He took it from my hand, walked over to the door, opened it, entered it, took out all the putrefying stuff that was rotting there, and threw it away. The He cleaned the closet and painted it, fixed it up, doing it all in a~moment's time. Oh, what victory and release to have that dead thing out of my life! 
\end{multicols}



\begin{multicols}{2}
    [
\section*{Transferring the Title}
    ]

Then a~thought came to me. I~said to myself, "I~have been trying to keep this heart of mine clear for Christ. I~start on one room and no sooner have I~cleaned that then another room is dirty. I~begin on the second room and the first room becomes dusty again. I~am so tired and weary trying to maintain a~clean heart and an obedient life. I~am just not up to it!" 

So I~ventured a~question: "Lord, is there any chance that You would take over the responsibility of the whole house and operate it for me and with me just as You did that closet? Would You take the responsibility to keep my heart what it ought to be and my life where it ought to be?" 

I~could see His face light up as He replied, "Certainly, that is what I~came to do. You cannot be a~victorious Christian in your own strength. That is impossible. Let me do it through you and for you. That is the way. But," He added slowly, "I~am not owner of this house. I~am just a~guest. I~have no authority to proceed, since the property is not mine." 

I~saw it in a~minute and dropping to my knees, I~said, "Lord, You have been a~guest and I~have been the host. From now on I~am going to be the servant. You are going to be the owner and Master and Lord." 

Running as fast as I~could to the strongbox, I~took out the title deed to the house describing its assets and liabilities, location and situation and condition. I~eagerly signed it over to belong to Him alone for time and eternity. "Here," I~said. "Here it is, all that I~am and have forever. Now You run the house. I'll just remain with You as a~servant and friend." 

He took my life that day and I~can give you my word, there is no better way to live the Christian life. He knows how to keep it in shape and deep peace settles down on the soul. May Christ settle down and be at home in your heart as Lord of all! 
\end{multicols}

\vfill
{\tiny This article is typesetted by the Navigators, Russia. Get additional copies from \ldots
}
\end{document}

